Error Summary (teaching-v2.0)

### 2020-12-02 script/R/preprocessor/error_summary.Rmd
add descriptions about excluded participants
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
removed old analysis and update error_summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("ggsignif")) {install.packages("ggsignif"); require("ggsignif")}
# statistics
if (!require("stats")) {install.packages("stats"); require("stats")}
if (!require("effsize")) {install.packages("effsize"); require("effsize")}
if (!require("ez")) {install.packages("ez"); require("ez")}

# function
source("./function.R")

# read a text file for ideal performance
dt_ideal <- read.table("./ideal.txt")
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = "./filtered/dt_correct_onset.txt", sep = ",")
dt_offset <- fread(file = "./filtered/dt_correct_offset.txt", sep = ",")
error_onset <- fread(file = "./filtered/error_onset.txt", sep = ",")
error_offset <- fread(file = "./filtered/error_offset.txt", sep = ",")
```

- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)

@@

## ONSET
### Corrected Error Onset (All)
```{r onset_all, echo = FALSE}
error_onset_all <- error_onset[CorrectionNr != "Exclude",]

@@

### Corrected Error Onset (Summary)
```{r onset_summary, echo = FALSE}
error_onset_all[startsWith(Reason, "Substituted")]$Reason <- "Substituted"
error_onset_summary <- error_onset_all[, .(N = .N, Sum = sum(as.numeric(CorrectionNr))), by = .(Reason)]
error_onset_summary
```

### Missing/Excluded Trials Onset (All)
```{r na_onset_all, echo = FALSE}
missing_onset <- checker(dt_onset, dt_ideal)
missing_onset
```

### Missing/Excluded Trials Onset (Summary)
```{r na_onset_summary, echo = FALSE}
missing_onset_summary <- missing_onset[, .(N = .N), by = .(Reason)]
missing_onset_summary
```

## OFFSET
### Corrected Error Offset (All)
```{r offset_all, echo = FALSE}
error_offset_all <- error_offset[CorrectionNr != "Exclude",]

@@

### Corrected Error Offset (Summary)
```{r offset_summary, echo = FALSE}
error_offset_all[startsWith(Reason, "Substituted")]$Reason <- "Substituted"
error_offset_summary <- error_offset_all[, .(N = .N, Sum = sum(as.numeric(CorrectionNr))), by = .(Reason)]
error_offset_summary
```

### Missing/Excluded Trials Offset (All)
```{r na_offset_all, echo = FALSE}
missing_offset <- checker(dt_offset, dt_ideal)
missing_offset
```

### Missing/Excluded Trials Offset (Summary)
```{r na_offset_summary, echo = FALSE}
missing_offset_summary <- missing_offset[, .(N = .N), by = .(Reason)]
missing_offset_summary
```

>>>>

# Workflow
1. filter with `filtering.R`
2. check the details of errors and remove some participants if needed (**this script**: `error_summary.Rmd`)
3. trim data (i.e., remove outliers) with `trimming.R`
4. check trimmed data and remove some participants if needed (`included_summary.Rmd`)

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("here")) {install.packages("here"); require("here")}

# set working directory
here::i_am("error_summary.Rmd")

# function
source(here("function.R"))

# read a text file for ideal performance
dt_ideal <- read.table(here("ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = here("filtered", "dt_correct_onset.txt"), sep = ",")
dt_offset <- fread(file = here("filtered", "dt_correct_offset.txt"), sep = ",")
error_onset <- fread(file = here("filtered", "error_onset.txt"), sep = ",")
error_offset <- fread(file = here("filtered", "error_offset.txt"), sep = ",")
```

# Design
- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)
- Note: SubNr 3 was excluded due to insufficient motor skills

@@

## ONSET
### Corrected Error Onset (All)
```{r onset-all, echo = FALSE}
error_onset_all <- error_onset[CorrectionNr != "Exclude"]

@@

### Corrected Error Onset (Summary)
```{r onset-summary, echo = FALSE}
error_onset_all[startsWith(Reason, "Substituted")]$Reason <- "Substituted"
error_onset_summary <- error_onset_all[, .(N = .N, Sum = sum(as.numeric(CorrectionNr))), by = .(Reason)]
error_onset_summary
```

### Missing/Excluded Trials Onset (All)
```{r na-onset-all, echo = FALSE}
missing_onset <- checker(dt_onset, dt_ideal)
missing_onset
```

### Missing/Excluded Trials Onset (Summary)
```{r na-onset-summary, echo = FALSE}
missing_onset_summary <- missing_onset[, .(N = .N), by = .(Reason)]
missing_onset_summary
```

## OFFSET
### Corrected Error Offset (All)
```{r offset-all, echo = FALSE}
error_offset_all <- error_offset[CorrectionNr != "Exclude",]

@@

### Corrected Error Offset (Summary)
```{r offset-summary, echo = FALSE}
error_offset_all[startsWith(Reason, "Substituted")]$Reason <- "Substituted"
error_offset_summary <- error_offset_all[, .(N = .N, Sum = sum(as.numeric(CorrectionNr))), by = .(Reason)]
error_offset_summary
```

### Missing/Excluded Trials Offset (All)
```{r na-offset-all, echo = FALSE}
missing_offset <- checker(dt_offset, dt_ideal)
missing_offset
```

### Missing/Excluded Trials Offset (Summary)
```{r na-offset-summary, echo = FALSE}
missing_offset_summary <- missing_offset[, .(N = .N), by = .(Reason)]
missing_offset_summary
```
